{\fontfamily{ptm}\selectfont Inexect Accelerated Proximal Gradient }

### 2025-09-30 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

            $\partial_\epsilon g$ is a multivalued operator and, it's not monotone, unless $\epsilon = 0$, which makes it equivalent to French subgradient $\partial g$. 

@@

        We develop the theory based on the use of epsilon subgradient as in Definition \ref{def:esp-subgrad}. 

@@

        \begin{lemma}[other representations of inexact proximal gradient]\;\\

@@

@@

@@

@@

@@

        \begin{fact}[minimizing dual of the proximal problem]

@@

                \Phi_{\lambda}(z_n) - \Phi_\lambda(\bar x) 

@@

        For this reasons, the inner loop interation required to achieve $\mathbf G(z_n, v_n) < \epsilon$ is now related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$. 
        \todoinline{
            STILL WRITING AND NOT FINISHED YET! 

@@

>>>>

            $\partial_\epsilon g$ is a multivalued operator and, it's not monotone, unless $\epsilon = 0$, which makes it equivalent to Fenchel subgradient $\partial g$. 

@@

        No, we develop the theory based on the use of epsilon subgradient as in Definition \ref{def:esp-subgrad}. 

@@

        \begin{lemma}[other representations of inexact proximal gradient]\;\label{lemma:other-repr-inxt-pg}\\

@@

            When $\epsilon = 0, \rho = 0$, this reduces to proximal gradient inequality in the exact case. 

@@

        Eventually we want to evaluate $T_{\rho}(x)$ of some $F = f + g$ inexactly and, by Lemma \ref{lemma:other-repr-inxt-pg}, one can achieve that through inexact evaluation of $\hprox_{\rho^{-1}g}$ in the sense of Definition \ref{def:inxt-pp}. 

@@

        \begin{align}\label{eqn:primal-pp}

@@

        \begin{align}\label{eqn:dual-pp}

@@

        \begin{fact}[minimizing dual of the proximal problem]\label{fact:minimizing-dual-pp}

@@

                \Phi_{\lambda}(z_n) - \Phi_\lambda(\bar z) 

@@

        For this reason, the number of iterations of the inner loop required to achieve $\mathbf G(z_n, v_n) < \epsilon$ for a given $e$ is related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$. 

@@

    In this section, we continue the discussion from \textcolor{red}{[REF PREVIOUS SECTION]}. 
    The inner loop of the algorithm evaluates $x_k \approx_\epsilon T_{(B + \rho)}(y_k)$ for a given value of $\epsilon$. 
    To attain $x_k$, one approach is to utilise Theorem \ref{thm:dlty-gap-inxt-pp} numerically, usually using iterative algorithms. 
    The following assumption places additional assumption to the proximal problem for the inner loop. 
    \begin{assumption}[gradient mapping error bound]\;\label{ass:pg-eb}\\
        The following assumption is about $(F, f, g, L, S, \gamma)$. 
        Assume that
            \item $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, 
            \item Let $\tau > 0$ be the step size inverse, let $T_{\tau}$ be the proximal operator of $f + g$ as given by $T_{\tau}(x) := \hprox_{\tau^{-1}g}(x - \tau^{-1}\nabla f(x))$, 
            \item the gradient mapping $\mathcal G_{\tau}$ be given by: $\mathcal G_t(x) = \tau (x - T_t(x))$, 
            \item $S= \argmin_{x}{f(x) + g(x)} \neq \emptyset$, 
            \item the objective function is given by $F = f + g$. 
        In addition, assume that the optimization problem $F$ satisfies the error bound condition if it has for all $\tau \ge L, x \in \RR^n$ there exists $\gamma > 0$: 
            \Vert \mathcal G_\tau(x)\Vert \ge \gamma\dist(x|S). 
    \begin{definition}[proximal gradient method]\label{def:ista}
        Suppose that $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}. 
        Let $\tau \ge L$, and $x_0 \in \RR^n$. 
        Then an algorithm is a proximal gradient method if it generates iterates $(x_k)_{k \ge 0}$ such that they satisfies for all $k \ge 1$: 
            x_{k + 1} = \hprox_{\tau^{-1} g}\left(x_k + \tau^{-1}\nabla f(x_k)\right). 
    \begin{assumption}[error bound for proximal problem]\;\label{ass:eb-for-pp}\\
        This assumption is about $(g, \omega, A, \Psi_\lambda, \gamma)$
        Here are the assumptions
            \item $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
            \item In addition, function $\Psi_\lambda$ as given by \eqref{eqn:primal-pp} satifies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2, g(v) = \omega(A v) - \frac{1}{2\lambda}\Vert y\Vert^2$. 
    \subsection{error bound and linear convergence}
        The following theorem characterize linear convergence of the proximal gradient method under gradient mapping error bound condition. 
        \begin{theorem}[linear convergence under gradient mapping error bound]\;\label{thm:lin-cnvg-ista-eb}\\
            Assume that $(F, f, g, L, S, \gamma)$ is given by Assumption \ref{ass:pg-eb}. 
            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ the inequality: 
                F(x_{k + 1}) - F(\bar x)
                    1 - \frac{\gamma}{2\tau}
                \right)(F(x_k) - F(\bar x)). 
            Hence, the algorithm generates $F(x_k) - F(\bar x)\le \mathcal O((1 - \gamma/(2\tau))^k)$. 
            Two important immediate results will be presented first.
            Consider the proximal gradient inequality from \ref{thm:inxt-pg-ineq}, but with $\rho = 0, \epsilon = 0, B = \tau$, then for all $x$ such that $\Vert \mathcal G_\tau(x)\Vert > 0$ it has for $\tilde x = T_{\tau}(x), z \in \RR^n$ the inequality 
                0 &\le 
                F(z) - F(\tilde x) + \frac{\tau}{2}\Vert x - z\Vert^2 - \frac{\tau}{2}\Vert z - \tilde x\Vert^2
                F(z) - F(\tilde x) - \frac{\tau}{2}\Vert x - \tilde x\Vert^2
                + \tau\langle x - z, x - \tilde x\rangle
                &= F(z) - F(\tilde x) - \frac{1}{2\tau}\Vert \mathcal G_\tau(x) \Vert^2
                + \langle x - z, \mathcal G_\tau(x)\rangle
                &\le F(z) - F(\tilde x) - \frac{1}{2\tau}\Vert \mathcal G_\tau(x)\Vert^2 
                + \Vert x - z\Vert \Vert \mathcal G_\tau(x)\Vert
                + \Vert \mathcal G_\tau(x)\Vert^2\left(
                    \frac{\Vert x - z \Vert}{\Vert \mathcal G_\tau(x)\Vert} - \frac{1}{2\tau}
            Now, for all $z = \bar x \in S$, from Assumption \ref{ass:eb-for-pp} it has
                \frac{\Vert x - z \Vert}{\Vert \mathcal G_\tau(x)\Vert}
                \frac{\Vert x - z \Vert}{\gamma \dist(x | S)} \le \frac{1}{\gamma}. 
            Hence for all $\bar x \in S$ it has 
            \begin{align}\label{ineq:lin-cnvg-ista-eb-pitem1}
                0\le F(\tilde x) - F(\bar x)&\le 
                \Vert \mathcal G_\tau(x)\Vert^2\left(
                    \frac{1}{\gamma} - \frac{1}{2\tau}
            Obviously it has $\gamma^{-1} - (1/2)\tau^{-1} > 0$. 
            When $z = x$, we have the inequality: 
            \begin{align}\label{ineq:lin-cnvg-ista-eb-pitem2}
                F(\tilde x) - F(x) &\le - \frac{1}{2\tau}\Vert \mathcal G_\tau(x)\Vert^2. 
            To derive the linear convergence, we use \eqref{ineq:lin-cnvg-ista-eb-pitem1} with $x = x_k, \tilde x = x_{k + 1}$:
            {\allowdisplaybreaks
                0 &\le 
                \Vert \mathcal G_\tau(x_k)\Vert^2\left(
                    \frac{1}{\gamma} - \frac{1}{2\tau} 
                - F(x_{k + 1}) + F(\bar x)
                \frac{1}{2\tau}\Vert \mathcal G_\tau(x_k)\Vert^2\left(
                    \frac{2\tau}{\gamma} - 1
                - F(x_{k + 1}) + F(\bar x)
                    \frac{2\tau}{\gamma} - 1
                    F(x_k) - F(x_{k + 1})
                - F(x_{k + 1}) + F(\bar x)
                    \frac{2\tau}{\gamma} - 1
                    F(x_k) - F(\bar x) + F(\bar x) - F(x_{k + 1})
                - F(x_{k + 1}) + F(\bar x)
                &= \frac{2\tau}{\gamma}(F(\bar x) - F(x_{k + 1}))
                + \left(
                    \frac{2\tau}{\gamma} - 1
                \right)(F(x_k) - F(\bar x)). 
            At (1) we used \eqref{ineq:lin-cnvg-ista-eb-pitem2}. 
            Multiple bothside by $\frac{\gamma}{2\tau}$ then we are done. 

    \subsection{characterizing linear convergence of the proximal problem}
